### 2018-04-26 papers/synth/encoding.tex
changes

\begin{align}
  \exists n, a, e, b, p, r, p,
  ( \texttt{Consistancy}\land \texttt{ActiveNode} \land 
  \texttt{ActiveEdge} \land \texttt{GivenCons} \land
  \texttt{ModifyCons} )   
  \tag{E1}\label{eq:addedge1}
\end{align}

@@

The basicvtsconstraints and vtsactivityconstraint are same as the
previous sections, describing stability of the graph and fusion of the
edge into the node and the molecular activity describing the active
state of a molecule. The givenvtsinformation is encoded using a front
end input language. The user provides the information of the VTS with
a partial information using this front end. Our tool then converts
these inputs into the constraints over the given VTS.

>>>>

\subsection{Encoding Incomplete VTS}

In our synthesis algorithm, we take a VTS $G =
(\nodes,\mols,\edges,\nlabel,\pairs,\edgef,\nodef)$ as input.
%
We allow activity functions not to be specified, i.e., vectors
$\edgef$ and $\nodef$ may contain uninterpreted Boolean functions.
%
We construct the following constraints to encode the available information
about $G$.
%
\begin{align*}
  \texttt{KnownE} &= \land \{e_{i,j,q,m}|(i,M_1,j),...,(i,M_{q'},j) \in \edges \land q \leq q' \land m \in M_q \}\\
  \texttt{KnownN} &= \land \{n_{i,m}| m \in \nlabel(i) \land i \in \nodes \}\\
  \texttt{KnownP} &= \land \{p_{i,j}| (i,j) \in \pairs \} \\
  \texttt{KnownActiveN} &= \land \{ a_{i,m} = \nodef_m (n_{i,1},\dots,n_{i,\mu}) | \nodef_m \text{ is defined.} \} \\
  \texttt{KnownActiveE} &= \land \{ b_{i,j,q,m} = \edgef_m(e_{i,j,q,1}, .., e_{i,j,q,\mu})
                   | \edgef_m \text{ is defined.} \} \\
  \texttt{KnownCons} & = \texttt{KnownE} \land \texttt{KnownN} \land 
                      \texttt{KnownP} \land \texttt{KnownActiveE} \land \texttt{KnownActiveN}
\end{align*}
We will do synthesis against the following property that says the VTS is stable and  3-connected,
but not 4-connected.
%
The property is designed to balance the search space such that the synthesis procedure does not
succeed with simply adding too many edges. 
%
\begin{align*}
  \texttt{Property} =  \texttt{Stability} \land \texttt{Connected}(3) \land \texttt{DisConnected}(4)
\end{align*}

Now we will consider the constraints for synthesis for the above
listed problems.
\begin{align*}
  \texttt{UnknownE} &= \{e_{i,j,q}|(i,M_1,j),...,(i,M_{q'},j) \in \edges \land 
                      q' < q \leq \pi \}\\
  \texttt{SynthE} &= \Sigma \texttt{UnknownE} \leq 3 \\
\end{align*}

\begin{align}
  \exists n, a, e, b, p
  ( \texttt{Consistancy}\land \texttt{Property} \land
  \texttt{KnownCons} \land \texttt{SynthCons} )
  \tag{E1}\label{eq:addedge1}
\end{align}

@@

% The basicvtsconstraints and vtsactivityconstraint are same as the
% previous sections, describing stability of the graph and fusion of the
% edge into the node and the molecular activity describing the active
% state of a molecule.The givenvtsinformation is encoded using a front
% end input language. The user provides the information of the VTS with
% a partial information using this front end. Our tool then converts
% these inputs into the constraints over the given VTS.

### 2018-04-26 papers/synth/prelim.tex
changes

\paragraph{Activity functions}
%
The following constraints encode that
the activity of the molecules are controlled by activity functions.
%
%
\begin{align}
\bigwedge\limits_{i,m} n_{i,m} \limplies a_{i,m} =  \nodef_m (n_{i,1},\dots,n_{i,\mu}) 
\tag{\texttt{ActiveNode}}\label{eq:anb}\\
   \bigwedge\limits_{i,j,q,m} e_{i,j,q,m} \limplies b_{i,j,q,m} = \edgef_k(e_{i,j,q,1}, .., e_{i,j,q,\mu} )
  \tag{\texttt{ActiveEdge}}\label{eq:aeb}
\end{align}
%
Later we will be synthesizing missing activity functions and replace the
above constraints with parameterized constraints.

@@

\paragraph{Stability property}
%
We use Boolean variable $r_{i,j,m,p}$ to indicate if there is an
$m$-path from $i$ to $j$ of length less than or equal to $p$.
%
We use $m$-reachability to encode the stability condition in VTSs.
%
The following constraint recursively encodes that node $j$ is $m$-reachable from node $i$ in less than $p$ steps.
%
Subsequently, we encode stability condition using the reachability variables.
\begin{align}
  \bigwedge\limits_{\mathclap{i,j,m,p}} r_{i,j,m,p} \limplies (\bigvee_{q} \, e_{i,j,q,m} \lor \bigvee_{i\neq i^{\prime}} ( \, \bigvee_{q} e_{i,i^{\prime},q,m}) \land r_{i^{\prime},j,m,p-1} )
  \tag{R1}\label{eq:reach1}\\
 \bigwedge\limits_{i,j,m} (\bigvee_{q} e_{i,j,q,m}) \limplies r_{j,i,m,\nu}
  \tag{R2}\label{eq:reach2}
\end{align}

\paragraph{$k$-connected property}
%
$k$-connectedness is a robustness property.
%
Let us use $d_{i,j,q}$ to indicate $q$th edge between $i$ and $j$ is dropped
and $r'_{i,j}$ to indicate if there is a path from $i$ to $j$ in
the modified VTS.
%
% To check whether $k$-connected is a
% necessary condition, we remove (drop) $k-1$ edges from the graph and
% if it disconnects the graph, and we get an assignment.
% %
% We have a graph that is not $k$-connected.
%
In the following, $\texttt{Drop}(d,k)$  encode that only
existing edges can be dropped and exactly $k-1$ edges are dropped.
%
$\texttt{Reach}(d,r')$ defines reachability in the modified VTS,
therefore we use a new variable $r'_{i,j}$ to encode reachability from
$i$ to $j$.
%
$\texttt{Connected}(r')$ says that all nodes are reachable from any
other node.
% In the following constraint, we encode $r'_{i,j}$ is true if there is an
% edge $(i,\_,j)$ and it is not dropped, or there is a node
% $i^{\prime}$ such that, there is an edge $(i,\_,i^{\prime})$ which is
% not dropped and $r'_{i',j}$ is true.
\begin{align*}
  \texttt{Drop}(d,k) = & 
  \bigwedge\limits_{i,j,q} d_{i,j,q} \limplies e_{i,j,q}  \land 
  \sum_{i,j,q} d_{i,j,q} = k-1\\
  \texttt{Reach}(d,r') = &
  \bigwedge\limits_{i,j}  [\bigvee_{q} (e_{i,j,q} \land  \neg d_{i,j,q}) \lor  (\bigvee_{i' \neq i}  r^{\prime}_{i',j} \land  \bigvee_{q} (e_{i,i',q} \land \neg d_{i,i',q}) ] \limplies r^{\prime}_{i,j}\\
  \texttt{Connected}(r') = & \Land\limits_{i,j} (r^{\prime}_{i,j} \lor r^{\prime}_{j,i})
\end{align*}
We will be synthesizing for both connected any disconnected graphs.
%
We also define the following macros. 
\begin{align*}
  \texttt{Connectedness}(k) = & \forall d.\;
          (\texttt{Drop}(d,k) \limplies \exists r'.\;\texttt{Reach}(d,r')
                                \land \texttt{Connected}(r'))\\
  \texttt{Disconnectedness}(k) = & \exists d.\;
          (\texttt{Drop}(d,k) \land \exists r'.\;\texttt{Reach}(d,r')
                                \land \lnot \texttt{Connected}(r'))
\end{align*}
Since the free variables in $\texttt{Connectedness}(k)$ are universally
quantified, please note that the connectedness property introduces the two
quantifier alternations.
%

>>>>

\paragraph{Activity functions}
We also need to encode that encode that
the activity of the molecules are controlled by activity functions.
%
However, the encoding functions can be given to us many different ways,
for example as a lookup table, or  a concise Boolean formula.
%
In the following constraints, we assume the appropriate encoding is
used for the functions.
%
\begin{align}
\bigwedge\limits_{i,m} n_{i,m} \limplies a_{i,m} =  \nodef_m (n_{i,1},\dots,n_{i,\mu}) 
\tag{\texttt{ActiveNode}}\label{eq:anb}\\
   \bigwedge\limits_{i,j,q,m} e_{i,j,q,m} \limplies b_{i,j,q,m} = \edgef_m(e_{i,j,q,1}, .., e_{i,j,q,\mu} )
  \tag{\texttt{ActiveEdge}}\label{eq:aeb}
\end{align}
%
Later we will be synthesizing missing activity functions and 
replace the above constraints with parameterized constraints that
encode a space of candidate functions.

\subsection{VTS properties}

@@

\paragraph{Stability property}
%
We use Boolean variable $r_{i,j,m,p}$ to indicate if there is an
$m$-path from $i$ to $j$ of length less than or equal to $p$.
%
We use $m$-reachability to encode the stability condition in VTSs.
%
The following constraint recursively encodes that node $j$ is $m$-reachable from node $i$ in less than $p$ steps.
%
Subsequently, we encode stability condition using the reachability variables.
\begin{align*}
  \texttt{paths}(r) &= \bigwedge\limits_{\mathclap{i,j,m,p}} r_{i,j,m,p} \limplies (\bigvee_{q} \, e_{i,j,q,m} \lor \bigvee_{i\neq i^{\prime}} ( \, \bigvee_{q} e_{i,i^{\prime},q,m}) \land r_{i^{\prime},j,m,p-1} )
  \\
  \texttt{loop}(r) &= \bigwedge\limits_{i,j,m} (\bigvee_{q} e_{i,j,q,m}) \limplies r_{j,i,m,\nu}
  \\
  \texttt{stability} &= \exists r. \; \texttt{paths}(r) \land \texttt{loop}(r)
\end{align*}

\paragraph{$k$-connected property}
%
$k$-connectedness is a robustness property.
%
Let us use $d_{i,j,q}$ to indicate $q$th edge between $i$ and $j$ is dropped
and $r'_{i,j}$ to indicate if there is a path from $i$ to $j$ in
the modified VTS.
%
% To check whether $k$-connected is a
% necessary condition, we remove (drop) $k-1$ edges from the graph and
% if it disconnects the graph, and we get an assignment.
% %
% We have a graph that is not $k$-connected.
%
In the following, $\texttt{Drop}(d,k)$  encode that only
existing edges can be dropped and exactly $k-1$ edges are dropped.
%
$\texttt{Reach}(d,r')$ defines reachability in the modified VTS,
therefore we use a new variable $r'_{i,j}$ to encode reachability from
$i$ to $j$.
%
$\texttt{Connected}(r')$ says that all nodes are reachable from any
other node.
% In the following constraint, we encode $r'_{i,j}$ is true if there is an
% edge $(i,\_,j)$ and it is not dropped, or there is a node
% $i^{\prime}$ such that, there is an edge $(i,\_,i^{\prime})$ which is
% not dropped and $r'_{i',j}$ is true.
\begin{align*}
  \texttt{Drop}(d,k) = & 
  \bigwedge\limits_{i,j,q} d_{i,j,q} \limplies e_{i,j,q}  \land 
  \sum_{i,j,q} d_{i,j,q} = k-1\\
  \texttt{ReachAbove}(d,r') = &
  \bigwedge\limits_{i,j}  [\bigvee_{q} (e_{i,j,q} \land  \neg d_{i,j,q}) \lor  (\bigvee_{i' \neq i}  r^{\prime}_{i',j} \land  \bigvee_{q} (e_{i,i',q} \land \neg d_{i,i',q}) ] \limplies r^{\prime}_{i,j}\\
  \texttt{ReachBelow}(d,r') = &
   \bigwedge\limits_{i,j}  r^{\prime}_{i,j} \limplies [\bigvee_{q} (e_{i,j,q} \land  \neg d_{i,j,q}) \lor  (\bigvee_{i' \neq i}  r^{\prime}_{i',j} \land  \bigvee_{q} (e_{i,i',q} \land \neg d_{i,i',q}) ]\\
  \texttt{Connected}(r') = & \Land\limits_{i,j} (r^{\prime}_{i,j} \lor r^{\prime}_{j,i})
\end{align*}
We will be synthesizing for both connected any disconnected graphs.
%
We also define the following macros. 
\begin{align*}
  \texttt{Connected}(k) = & \forall d.\;
          (\texttt{Drop}(d,k) \limplies \exists r'.\;\texttt{ReachBelow}(d,r')
                                \land \texttt{Connected}(r'))\\
  \texttt{Disconnected}(k) = & \exists d.\;
          (\texttt{Drop}(d,k) \land \exists r'.\;\texttt{ReachAbove}(d,r')
                                \land \lnot \texttt{Connected}(r'))
\end{align*}
Since the free variables in $\texttt{Connectedness}(k)$ are universally
quantified, please note that the connectedness property introduces the two
quantifier alternations.
%
